|

### 2023-05-08 paper/01-introduction.Rmd
edits/comments on intro section

We contribute to the growing literature of research based on player tracking data in American football. The National Football League (NFL) introduced their player tracking system known as [Next Gen Stats (NGS)](https://operations.nfl.com/gameday/technology/nfl-next-gen-stats/) in 2016, using radio frequency identification (RFID) chips placed in players' shoulder pads (and in the ball) to collect data 10 times per second. These NGS tracking data contain information about the on-field locations, speeds, and angles of all 22 players on the field (as well as the ball). While these data were initially only available for teams, media, and vendors, in December 2018 the NFL launched the inaugural edition of their annual [Big Data Bowl (BDB)](https://operations.nfl.com/gameday/analytics/big-data-bowl/past-big-data-bowl-recaps/) competition.

@@

>>>>

<!-- We contribute to the growing literature of research based on player tracking data in American football.  -->

In an attempt to foster analytics and innovate the game, the National Football League (NFL) introduced their player tracking system known as [Next Gen Stats (NGS)](https://operations.nfl.com/gameday/technology/nfl-next-gen-stats/) in 2016, using radio frequency identification (RFID) chips placed in players' shoulder pads (and in the ball) to collect data 10 times per second. These NGS tracking data contain information about the on-field locations, speeds, and angles of all 22 players on the field (as well as the ball). While these data were initially only available for teams, media, and vendors, in December 2018 the NFL launched the inaugural edition of their annual [Big Data Bowl (BDB)](https://operations.nfl.com/gameday/analytics/big-data-bowl/past-big-data-bowl-recaps/) competition.

@@

[I think we need a couple of paragraphs here to introduce the defensive linemen position, and the role/significance of linemen, why is it important to analyze them]
